\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-17 4-1-basic.Rmd
weatherdata sentences cleaned up

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{weatherdata::historical_tmax} is a subset containing the records of maximum temperature for `r nrow(historical_tmax)` Australian stations from `r range(historical_tmax$first_year)[1]` through `r range(historical_tmax$first_year)[2]` and provides information also on the latitude, longitude and elevation of each of the  stations. This data  is already cast into a \code{cubble} data object (please see Appendix X for the code to extract  the data from XX and prepare the data into \code{cubble} form), with \code{id} as the key, \code{date} as the index, and \code{c(longitude, latitude)} as the coordinates. The goal of this example is to compare the monthly average maximum temperature  between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.

>>>>

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{historical_tmax} is a subset containing the records of maximum temperature for `r nrow(historical_tmax)` Australian stations from `r range(historical_tmax$first_year)[1]` through `r range(historical_tmax$first_year)[2]` and provides information also on the latitude, longitude and elevation of each of the  stations, extracted using the `rnoaa` package. <!-- This data  is already cast into a \code{cubble} data object (please see Appendix X for the code to extract  the data from XX and prepare the data into \code{cubble} form), with \code{id} as the key, \code{date} as the index, and \code{c(longitude, latitude)} as the coordinates.--> The goal of this example is to compare the monthly average maximum temperature  between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.

### 2022-06-17 jss/cubble-jss.tex
appendix
weatherdata sentences cleaned up

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{weatherdata::historical_tmax} is a subset containing the records of maximum temperature for 236 Australian stations from 1859 through 1969 and provides information also on the latitude, longitude and elevation of each of the stations. This data is already cast into a \code{cubble} data object (please see Appendix X for the code to extract the data from XX and prepare the data into \code{cubble} form), with \code{id} as the key, \code{date} as the index, and \code{c(longitude, latitude)} as the coordinates. The goal of this example is to compare the monthly average maximum temperature between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.

>>>>

The Global Historical Climatology Network (GHCN) provides daily climate measures from stations across the world. The data \code{historical_tmax} is a subset containing the records of maximum temperature for 236 Australian stations from 1859 through 1969 and provides information also on the latitude, longitude and elevation of each of the stations, extracted using the \texttt{rnoaa} package. The goal of this example is to compare the monthly average maximum temperature between two periods, 1971-1975 and 2016-2020, for stations in Victoria and New South Wales.
